Supplementary Information

### 2021-01-09 doc/manuscript/MEE_manuscript_SI.Rmd
added new figures to SI

all_GLS = "S9-S18"
GLS_BCNM = "S9"
GLS_HKK = "S10"
GLS_SCBI = "S11"
GLS_LDW = "S12"
GLS_HF = "S13"
GLS_ZOF = "S14"
GLS_NE = "S15"
GLS_LT = "S16"
GLS_CB = "S17"
GLS_SC = "S18"

@@

GLS_BCNM_legend = "Figure S9. Best GLS models for Barro Colorado Nature Monument (Panama)"
GLS_HKK_legend = "Figure S10. Best GLS models for Huai Kha Khaeng (Thailand)"
GLS_SCBI_legend = "Figure S11. Best GLS models for the Smithsonian Conservation Biology Institute (Virginia, USA)"
GLS_LDW_legend = "Figure S12. Best GLS models for Lilley Dickey Woods (Indiana, USA)"
GLS_HF_legend = "Figure S13. Best GLS models for Harvard Forest (Massachusetts, USA) "
GLS_ZOF_legend = "Figure S14. Best GLS models for Zofin Forest (Czech Republic)"
GLS_NE_legend = "Figure S15. Best GLS models for Niobrara/ Halsey (Nebraska, USA)"
GLS_LT_legend = "Figure S16. Best GLS models for Little Tesuque (New Mexico, USA)"
GLS_CB_legend = "Figure S17. Best GLS models for Cedar Breaks (Utah, USA)"
GLS_SC_legend = "Figure S18. Best GLS models for Scotty Creek (Northwest Territory, Canada)"

@@

![`r GLS_BCNM_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/BCI.png){ width=75% }

@@

![`r GLS_HKK_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/HKK.png){ width=75% }

@@

![`r GLS_SCBI_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/SCBI.png){ width=75% }

@@

![`r GLS_LDW_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/LillyDickey.png){ width=75% }

@@

![`r GLS_HF_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/HarvardForest.png){ width=75% }

@@

![`r GLS_ZOF_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/Zofin.png){ width=75% }

\newpage
## `r GLS_NE_legend`

![`r GLS_NE_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/Nebraska.png){ width=75% }

@@

![`r GLS_LT_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/NewMexico.png){ width=75% }

@@

![`r GLS_CB_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/CedarBreaks.png){ width=75% }

@@

![`r GLS_SC_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/ScottyCreek.png){ width=75% }

>>>>

all_GLS = "S9-S28"
GLS_BCNM = "S9"
GLS_BCNM_year = "S10"
GLS_HKK = "S11"
GLS_HKK_year = "S12"
GLS_SCBI = "S13"
GLS_SCBI_year = "S14"
GLS_LDW = "S15"
GLS_LDW_year = "S16"
GLS_HF = "S17"
GLS_HF_year = "S18"
GLS_ZOF = "S19"
GLS_ZOF_year = "S20"
GLS_NIO = "S21"
GLS_NIO_year = "S22"
GLS_LT = "S23"
GLS_LT_year = "S24"
GLS_CB = "S25"
GLS_CB_year = "S26"
GLS_SC = "S27"
GLS_SC_year = "S28"

SC_1970break = "S29"

RW_interactions_all= "S30"
BAI_interactions_all= "S31"

@@

# without year
GLS_BCNM_legend = "Figure S9. Best GLS models including climate and DBH for Barro Colorado Nature Monument (Panama)"
GLS_BCNM_year_legend = "Figure S10. Best GLS models including climate, DBH, and year for Barro Colorado Nature Monument (Panama)"
GLS_HKK_legend = "Figure S11. Best GLS models including climate and DBH for Huai Kha Khaeng (Thailand)"
GLS_HKK_year_legend = "Figure S12. Best GLS models including climate, DBH, and year for Huai Kha Khaeng (Thailand)"
GLS_SCBI_legend = "Figure S13. Best GLS models including climate and DBH for the Smithsonian Conservation Biology Institute (Virginia, USA)"
GLS_SCBI_year_legend = "Figure S14. Best GLS models including climate, DBH, and year for the Smithsonian Conservation Biology Institute (Virginia, USA)"
GLS_LDW_legend = "Figure S15. Best GLS models including climate and DBH for Lilley Dickey Woods (Indiana, USA)"
GLS_LDW_year_legend = "Figure S16. Best GLS models including climate, DBH, and year for Lilley Dickey Woods (Indiana, USA)"
GLS_HF_legend = "Figure S17. Best GLS models including climate and DBH for Harvard Forest (Massachusetts, USA) "
GLS_HF_year_legend = "Figure S18. Best GLS models including climate, DBH, and year for Harvard Forest (Massachusetts, USA) "
GLS_ZOF_legend = "Figure S19. Best GLS models including climate and DBH for Zofin Forest (Czech Republic)"
GLS_ZOF_year_legend = "Figure S20. Best GLS models including climate, DBH, and year for Zofin Forest (Czech Republic)"
GLS_NIO_legend = "Figure S21. Best GLS models including climate and DBH for Niobrara (Nebraska, USA)"
GLS_NIO_year_legend = "Figure S22. Best GLS models including climate, DBH, and year for Niobrara (Nebraska, USA)"
GLS_LT_legend = "Figure S23. Best GLS models including climate and DBH for Little Tesuque (New Mexico, USA)"
GLS_LT_year_legend = "Figure S24. Best GLS models including climate, DBH, and year for Little Tesuque (New Mexico, USA)"
GLS_CB_legend = "Figure S25. Best GLS models including climate and DBH for Cedar Breaks (Utah, USA)"
GLS_CB_year_legend = "Figure S26. Best GLS models including climate, DBH, and year for Cedar Breaks (Utah, USA)"
GLS_SC_legend = "Figure S27. Best GLS models including climate and DBH for Scotty Creek (Northwest Territory, Canada)"
GLS_SC_year_legend = "Figure S28. Best GLS models including climate, DBH, and year for Scotty Creek (Northwest Territory, Canada)"

SC_1970break_legend = "Figure 29. Climate responses at Scotty Creek (Northwest Territory, Canada) before and after 1970."

RW_interactions_all_legend = "Figure S30. (RW_interactions_all)"
BAI_interactions_all_legend ="Figure S31. (BAI_interactions_all)"

@@

![`r GLS_BCNM_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/BCI.png){ width=90% }

\newpage
## `r GLS_BCNM_year_legend`

![`r GLS_BCNM_year_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/BCI_with_Year.png){ width=90% }

@@

![`r GLS_HKK_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/HKK.png){ width=90% }

\newpage
## `r GLS_HKK_year_legend`

![`r GLS_HKK_year_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/HKK_with_Year.png){ width=90% }

@@

![`r GLS_SCBI_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/SCBI.png){ width=90% }

\newpage
## `r GLS_SCBI_year_legend`

![`r GLS_SCBI_year_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/SCBI_with_Year.png){ width=90% }

@@

![`r GLS_LDW_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/LillyDickey.png){ width=90% }

\newpage
## `r GLS_LDW_year_legend`

![`r GLS_LDW_year_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/LillyDickey_with_Year.png){ width=90% }

@@

![`r GLS_HF_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/HarvardForest.png){ width=90% }

\newpage
## `r GLS_HF_year_legend`

![`r GLS_HF_year_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/HarvardForest_with_Year.png){ width=90% }

@@

![`r GLS_ZOF_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/Zofin.png){ width=90% }

\newpage
## `r GLS_ZOF_year_legend`

![`r GLS_ZOF_year_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/Zofin_with_Year.png){ width=90% }

\newpage
## `r GLS_NIO_legend`

![`r GLS_NIO_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/Niobara.png){ width=90% }

\newpage
## `r GLS_NIO_year_legend`

![`r GLS_NIO_year_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/Niobara_with_Year.png){ width=90% }

@@

![`r GLS_LT_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/NewMexico.png){ width=90% }

\newpage
## `r GLS_LT_year_legend`

![`r GLS_LT_year_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/NewMexico_with_Year.png){ width=90% }

@@

![`r GLS_CB_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/CedarBreaks.png){ width=90% }

\newpage
## `r GLS_CB_year_legend`

![`r GLS_CB_year_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/CedarBreaks_with_Year.png){ width=90% }

@@

![`r GLS_SC_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/ScottyCreek.png){ width=90% }

\newpage
## `r GLS_SC_year_legend`

![`r GLS_SC_year_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/ScottyCreek_with_Year.png){ width=90% }

## `r SC_1970break_legend`

**(a) pre-1970**

![](tables_figures/SI_figures/GLS_pre1970_ScottyCreek.png){ width=70% }

**(b) post-1970**

![`r SC_1970break_legend`](tables_figures/SI_figures/GLS_post1970_ScottyCreek.png){ width=70% }

\newpage
## `r RW_interactions_all_legend`

![`r RW_interactions_all_legend`](tables_figures/pre_temp_groups_dbh_interactions_log_core_measurement_dbh.png){ width=100% }

\newpage
## `r BAI_interactions_all_legend`

![`r BAI_interactions_all_legend`](tables_figures/pre_temp_groups_dbh_interactions_log_BAI_dbh.png){ width=100% }
